Supplemental Materials for the paper: \\Pesticides pollution of small streams in Germany

### 2016-07-29 article.tex
rerun all, checked for smooth interaction, add raw plot of rac exceedances

National monitoring programs are setup for determination and surveillance of the chemical and ecological status of surface, ground and drinking water.
These monitoring programs produce huge amounts of data, which possibly can also be used to answer other questions.
In Germany monitoring programs are setup by the federal states in compliance with the Water Framework Directive \citep{quevauviller_water_2008} and further state specific needs.
However, currently there is no curated national-wide compilation of this data.

@@

All data-processing and analyses have been performed using R, version 3.3.1 \citep{r_core_team_r:_2016}.
To display differences in the spectra of analysed compounds between federal states we used Multidimensional Scaling (MDS) based on Jaccard dissimilarity in conjunction with hierarchical clustering using the vegan package \citep{oksanen_vegan:_2016}.
We expected non-linear responses to agriculture and catchment size and therefore, used generalized additive models (GAM) to identify relationships \todo{citation fewster}.

@@

where $No_i$ is the observed number of exceedances at site $i$, $Agri_i$ the proportion of agriculture within the catchment and $Size_i$ the catchment size of the site. 
We used the number of samplings ($n_i$) as an offset to account different sampling efforts. 
We modeled $No_i$ as resulting from a negative binomial distribution ($NB$).
$f_1$ and $f_2$ are smoothing functions using thin plate regression splines \citep{wood_thin_2003}.
The degree of smoothness was estimated using restricted maximum likelihood (REML) during model fitting process \citep{wood_fast_2011}.
Similar models were fitted to the number of EQS-exceedances and the 95th percentile of $log(TU_{max})$ (see Supplement for details).
GAM were fitted using the mgcv package \citep{wood_fast_2011}.

>>>>

National monitoring programs are setup for determination and surveillance of the chemical and ecological status of surface, ground and drinking water.
These monitoring programs produce large amounts of data, which possibly can also be used to answer other questions.
In Germany monitoring programs are setup by the federal states in compliance with the Water Framework Directive \citep{quevauviller_water_2008} and further state specific needs.
However, currently there is no curated national-wide compilation of this data.

@@

All data-processing and analyses have been performed using R, version 3.3.1 \citep{r_core_team_r:_2016}.
To display differences in the spectra of analysed compounds between federal states we used Multidimensional Scaling (MDS) based on Jaccard dissimilarity in conjunction with hierarchical clustering using the vegan package \citep{oksanen_vegan:_2016}.
We expected non-linear responses to agriculture and catchment size and therefore, used generalized additive models (GAM) to identify relationships \citep{fewster_analysis_2000}.

@@

where $No_i$ is the observed number of exceedances at site $i$, $Agri_i$ the proportion of agriculture within the catchment and $Size_i$ the catchment size of the site. 
We used the number of samplings ($n_i$) as an offset to account different sampling efforts. 
We modeled $No_i$ as resulting from a negative binomial distribution ($NB$).
$f_1$ and $f_2$ are smoothing functions using thin plate regression splines \citep{wood_thin_2003}.
The degree of smoothness was estimated using restricted maximum likelihood (REML) during model fitting process \citep{wood_fast_2011}.
Similar models were fitted to the number of EQS-exceedances and the 95th percentile of $log(TU_{max})$ (see Supplement for details). \todo{TRUE?}
GAM were fitted using the mgcv package \citep{wood_fast_2011}.

### 2016-07-29 supplement/Supplemental_Materials.tex
supplement + ms
completed overview
rerun all, checked for smooth interaction, add raw plot of rac exceedances

\documentclass[pdftex,a4paper]{scrreprt}
\usepackage[utf8]{inputenc}       
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{booktabs}

\usepackage[
	round,	%(defaultage in the main file and \input ) for round parentheses;
	authoryear,% (default) for author-year citations;
	sort,		% orders multiple citations into the sequence in which they 
]{natbib}	
\usepackage{csvsimple}  % read csv files into Latex

@@

@@

\chapter{Overview on compiled data}

% table generate in do_overview.R
\input{phchoverview}

>>>>

\documentclass[pdftex,a4paper]{scrreprt}
\usepackage[utf8]{inputenc}       
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{booktabs} % table rulers
\usepackage{longtable} % multipage tables
\usepackage{todonotes}

\usepackage[
	round,	%(defaultage in the main file and \input ) for round parentheses;
	authoryear,% (default) for author-year citations;
	sort,		% orders multiple citations into the sequence in which they 
]{natbib}

@@

\tableofcontents
\listoffigures
\listoftables

@@

\chapter{Overview on compiled data}
% Overview samples
% table generated in do_overview.R
\input{phchoverview}

\begin{figure}
	\centering
	\includegraphics[width = 0.8\textwidth]{varclus}
	\caption{Complete Linkage Cluster Dendrogram of Jaccard Similarity of analysed compound spectra between federal states. Abbreviations of state names according to ISO 3166-2:DE.}
	\label{fig:varclus}
\end{figure}

% Overview variables
% table generated in do_overview.R
\input{phchvar}

\begin{figure}
	\centering
	\includegraphics[width = 0.75\textwidth]{precip}
	\caption{Distribution of precipitation at sampling occasions. top: at sampling date. bottom: at day before sampling.}
	\label{fig:precip}
\end{figure}

\chapter{Are small agricultural waters more polluted compared to bigger streams?}

\begin{figure}
	\centering
	\includegraphics[width = 0.8\textwidth]{ezgagrirac}
	\caption{Raw data used for the model in equation xxx and Figure xxx of the main article. Color codes the number of RAC exceedances (on a log-scale). Grey points are sites without any exceedance.}
	\label{fig:ezgagrirac}
\end{figure}
\todo{update refs}
